Efficient Community Formation \\ for Web Services

### 2014-01-12 papers/coalition-journal-R1/coalition_journal_r1.tex
changes

\textbf{Web Service Community.}
Communities of web services are a collection of web services with same functionallity having a 
coordinator or service broker as manager and also the access point to the community. In \cite{DBLP:journals/internet/BenatallahSD03}, Behatallah et al. defined communities as \emph{Service Containers} which aggregates substitutable web services providing a common functionality (same set of operations). They abstracted \emph{Service Containers} as web services which are created, advertised, discovered and invoked just as elementary web services, they \emph{Container} as a manager is responsible for the mentioned tasks and also web service selection upon recieving a request on run-time. They have proposed a scoring service based on non-functional requrement of the task and web service capabilties to dynamicly chose the web service to perform the task upon reciving requests. A similar concept was proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}. They introduced web service coimmunities as a collection of web services with a common functionality but different QoS properties. A community manager upon recieving a request, delegates the request to one of its current members. The choice is based on history and quality metrics of each web service. They have proposed an efficient global web service selection algorithm in order to approach quality constraints and preferences for composite services which requres aggregation of different type of services to satisfy a request.

Benslimane et al. \cite{Liris-2770} have proposed a multi-layer approach, grouping similar Web services into communities and having an interface implemented as an asbtract Web service for accessing the community on top of the community layer. The intractions between composite, management and community layers and the bindings are performed by a generic driver called Open Software Connectivity (OSC).

Authors in \cite{managing-hela-jalel} have proposed web service communities with centralized access accross distributed web services. They have proposed a framework for web service management, query resolution among communities and a query caching mechanism to improve the performance of query resolution process among many distributed communities by caching previous computed results for answering future quries.

@@

In \cite{Medjahed05adynamic} authors developed a community as a ``container'' that clusters Web services based on a specefic area of interest. All web services in a given community, share the same functionality. These communities are created by \emph{third party community prividers} which use the \emph{community ontology} as a template and define a set of operations that all web services within a community should provide. Using semantic analysis on web service operations, web services either find and join a community with similar functionality or create a new operation description for a new community.

@@

In fact, it is possible to develop an algorithm that continues the
verification of this condition against subsets of size $3$, $4$,
etc. until the algorithm gets interrupted becuase of time constraint. If the algorithm gets intreupted while verification \emph{Depth(n)} conditions, we will have \emph{Depth(n-1)} results.

@@

The solution we propose for communities to ensure  stability is
applying a tax $\epsilon$, which is an amount of cost for those
web services that decide to change communities, which would make
deviation a costly act. However, this would require all the
community coordinators to agree on a same amount of taxation,
being governed by some external entities; otherwise, web services
would join communities charging the lowest amount of tax. Another
viable solution we introduce to our scenario is to stabilize the
game using external subsidies. The reason a game is not stable is
that the community is not making enough revenue to allocate enough
gain to the players. A community coordinator can subside its community
with a constant coefficient value of $\lambda$.
%
%Rewarding a community with high number of quality participants
%with $\lambda v(C)$, where $\lambda \leq 1$.
%
Obviously, with a big value for $\lambda$, it is always possible
to stabilize the community. However, this can be a costly act for
the community coordinators, so they are interested in the minimum
subside value of $\lambda$ making the community stable. When a new web service $i$, wants to join the community, the valuation function of the community members and the new web service is subsided by the community coordinator in order to incentivize formation of this community and is set to:
\begin{equation}\label{taxv}
v'(C \cup \{i\}) = \lambda \times v(C \cup \{i\})
\end{equation}
In equation \ref{eq:taxv} the value of $v'$ is replaced with the valuation function for the new forming coalition $C \cup \{i\}$.
Subsiding or taxing in order to reduce the bargaining power of sub
coalitions are called $taxation$ \cite{eps346856} methods. We
evaluate the effectiveness of these two methods experimentally
through extensive implementations in the next section.

@@

For the \emph{optimal core} method, we have used the well known
\emph{$\epsilon$-core} method as the taxation method to relax the
core condition to help communities attract web services. We have
assigned $\epsilon$ to 15\% of total community worth, which means
$\epsilon = 0.15 \times v(C)$. This allows subsets of the
coalition to gain maximum 15\% of $v(C)$. In the \emph{optimal
$\epsilon$-core} method, we capped the coalition size to 25 web
services, since the method is computationally intractable as the
number of web services increases. In fact, given the machine
configuration we used in our simulation, the maximum number we
could run for this method is 25. In the other methods, there were
no cap on size of the community and we had communities of size 160
web services at some points. In this scenario, our community
receives 130 tasks from users on average per iteration. These tasks are randomly generated and are expected to be performed by the community. Depending on community task queue and the assigned web services' quality metrics the task will be performed with some qualities.
The community, after the task distribution process on each iteration,
will reevaluate QoS metrics of its members and can check for new
membership requests. Web services may join or leave the community
between iterations. The results show that our \emph{depth-2 convex
checker} method is performing better compared to the other methods
and its performance is close to the optimal \emph{$\epsilon$-core}
method. Our \emph{depth-1 convex checker} and the \emph{3-Way
Satisfaction} method, are also performing well.

>>>>

\textbf{Web Service Community.}
Communities of web services are a collection of web services with same functionality sharing a
coordinator or service broker as manager which also serves as the access point to the community. Web service communities facilitate the discovery of web services and also provide services with better quality.

As an example, let us consider major air liners providing ticket selling service. We can consider them as competing agents, which each try to maximize their utilities by gaining more of the market share. However, major airliners, can collaborate if the collaboration would be beneficial for \emph{all} the agents. By sharing resources and also market share and also having the option of service multi-hop air tickets combined from different air liners, both air liners can increase their gain by collaborating. The question is when this collaboration would be beneficial for all the agents involved? For example major airliners would not gain anything by collaborating and sharing resources with airliners of low reputation and quality. They will lose their market and would rather stay away from this collaboration, therefore no stable cooperation can form between them.

In \cite{DBLP:journals/internet/BenatallahSD03}, Behatallah et al. defined communities as \emph{Service Containers} which aggregates substitutable web services providing a common functionality (same set of operations). They abstracted \emph{Service Containers} as web services which are created, advertised, discovered and invoked just as elementary web services, they \emph{Container} as a manager is responsible for the mentioned tasks and also web service selection upon receiving a request on run-time. They have proposed a scoring service based on non-functional requirement of the task and web service capabilities to dynamically chose the web service to perform the task upon receiving requests. A similar concept was proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}. They introduced web service communities as a collection of web services with a common functionality but different QoS properties. A community manager upon receiving a request, delegates the request to one of its current members. The choice is based on history and quality metrics of each web service. They have proposed an efficient global web service selection algorithm in order to approach quality constraints and preferences for composite services which requires aggregation of different type of services to satisfy a request.

Benslimane et al. \cite{Liris-2770} have proposed a multi-layer approach, grouping similar Web services into communities and having an interface implemented as an abstract Web service for accessing the community on top of the community layer. The interactions between composite, management and community layers and the bindings are performed by a generic driver called Open Software Connectivity (OSC).

Authors in \cite{managing-hela-jalel} have proposed web service communities with centralized access across distributed web services. They have proposed a framework for web service management, query resolution among communities and a query caching mechanism to improve the performance of query resolution process among many distributed communities by caching previous computed results for answering future queries.

@@

In \cite{Medjahed05adynamic} authors developed a community as a ``container'' that clusters Web services based on a specific area of interest. All web services in a given community, share the same functionality. These communities are created by \emph{third party community providers} which use the \emph{community ontology} as a template and define a set of operations that all web services within a community should provide. Using semantic analysis on web service operations, web services either find and join a community with similar functionality or create a new operation description for a new community.

@@

In fact, it is possible to develop an algorithm that continues the
verification of this condition against subsets of size $3$, $4$,
etc. until the algorithm gets interrupted becuase of time constraint. If the algorithm gets intreupted while verifying \emph{Depth(n)} conditions, it will have \emph{Depth(n-1)} verified.

@@

The solution we propose for communities to ensure  stability is
applying a tax $\epsilon$, which is an amount of cost for those
web services that decide to change communities, which would make
deviation a costly act. However, this would require all the
community coordinators to agree on a same amount of taxation,
being governed by some external entities; otherwise, web services
would join communities charging the lowest amount of tax. Another
viable solution we introduce to our scenario is to stabilize the
game using external subsidies. The reason a game is not stable is
that the community is not making enough revenue to allocate enough
gain to the players. A community coordinator can subside its community
with a constant coefficient value of $\lambda$.
%
%Rewarding a community with high number of quality participants
%with $\lambda v(C)$, where $\lambda \leq 1$.
%
Obviously, with a big value for $\lambda$, it is always possible
to stabilize the community. However, this can be a costly act for
the community coordinators, so they are interested in the minimum
subside value of $\lambda$ making the community stable. When a new web service $i$, wants to join the community, the valuation function of the community members and the new web service is subsided by the community coordinator in order to incentivize formation of this community and is set to:
\begin{equation}\label{eq:taxv}
v'(C \cup \{i\}) = \lambda \times v(C \cup \{i\})
\end{equation}
In equation \ref{eq:taxv} the value of $v'$ is replaced with the valuation function for the new forming coalition $C \cup \{i\}$.
Subsiding or taxing in order to reduce the bargaining power of sub
coalitions are called $taxation$ \cite{eps346856} methods. We
evaluate the effectiveness of these two methods experimentally
through extensive implementations in the next section.

@@

For the \emph{optimal core} method, we have used the well known
\emph{$\epsilon$-core} method as the taxation method to relax the
core condition to help communities attract web services. We have
assigned $\epsilon$ to 15\% of total community worth, which means
$\epsilon = 0.15 \times v(C)$. This allows subsets of the
coalition to gain maximum 15\% of $v(C)$. In the \emph{optimal
$\epsilon$-core} method, we capped the coalition size to 25 web
services, since the method is computationally intractable as the
number of web services increases. In fact, given the machine
configuration we used in our simulation, the maximum number we
could run for this method is 25. In the other methods, there were
no cap on size of the community and we had communities of size 160
web services at some points. 
In the experiments, \emph{Depth-1 Convex-Checker} and \emph{Depth-2 Convex-Checker} methods generate results instantly (0ms in Java millisecond time unit granularity) in our machines since their runtime to the size of input (number of web services) is $O(n)$ and $O(n^2)$ respectively, therefore they suffer no scalability issues.
In this scenario, our community
receives 130 tasks from users on average per iteration. These tasks are randomly generated and are expected to be performed by the community. Depending on community task queue and the assigned web services' quality metrics the task will be performed with some qualities.
The community, after the task distribution process on each iteration,
will reevaluate QoS metrics of its members and can check for new
membership requests. Web services may join or leave the community
between iterations. The results show that our \emph{depth-2 convex
checker} method is performing better compared to the other methods
and its performance is close to the optimal \emph{$\epsilon$-core}
method. Our \emph{depth-1 convex checker} and the \emph{3-Way
Satisfaction} method, are also performing well.
